On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-07 main.tex
Minor typos in S2

Even if $f$ does not satisfy $\textbf{H}_i$, we mentioned that it
does, after applying a generic change of variables. The precise
statement is the following; to state it, we use the following
notation. For a matrix $\mA$ in $\C^{n\times n}$ and $g$ in
$\C[X_1,\hdots,X_n]$ we write $g^\mA:=g(\mA \Xb) \in
\C[X_1,\dots,X_n]$, where $\Xb$ is the column vector with entries
$X_1,\dots,X_n$.

>>>>

Even if $f$ does not initially satisfy $\textbf{H}_i$, it does after applying a generic change of variables. The precise
statement is as follows, for which we use the following
notation. For a matrix $\mA$ in $\C^{n\times n}$ and $g$ in
$\C[X_1,\hdots,X_n]$ we write $g^\mA:=g(\mA \Xb) \in
\C[X_1,\dots,X_n]$, where $\Xb$ is the column vector with entries
$X_1,\dots,X_n$.
